Draft

### 2017-03-29 Draft/sections/misc-physics.tex
Some micellaneous useful physical ponts.
[minor] Why we should Fourier-transform Creation/Annihilation operator like that!

For the book \cite{griffiths-EM}, pp. 120 of section 3.1.6.

>>>>

For the book \cite{griffiths-EM}, pp. 120 of section 3.1.6. 
\subsection{Fourier transformation of Creation and Annihilation
Operators}
\label{sec:Fourier-CreationAnnihilation}
There is one pitfall when dealing with fourier transformation of creation or
annihilation operators. Suppose we have (for fermions):
\begin{equation}
    c_k = \sum_m e^{-ikm} c_m
    \label{eq:fourier-ck}
\end{equation}
(ignoring all unnecessary normalization factors)
Then there are two ways to process the fourier transformation of $c^\dagger_m$:

\textbf{First}, we could start with mathematical precision, and define:
\begin{equation}
    \mathcal{F}[c^\dagger_m](k) \equiv \sum_m e^{-ikm}c^\dagger_m
\end{equation}
\textbf{Second}, we could instead define:
\begin{equation}
    c^\dagger_k \equiv \sum_m e^{ikm} c^\dagger_m
    \label{eq:fourier-cDaggerK}
\end{equation}
The second definition is most encountered in physics literature, because it has
several benefits. The first is that it is intuitively straightforward to proceed
from eq.\ref{eq:fourier-ck} to eq.\ref{eq:fourier-cDaggerK}. The second point is
that, the second definition preserves the commutation relationship. It is
straightforward to get,
\begin{align}
    \{c_k,c^\dagger_{k'}\} &= \delta_{k,k'} \\
    \{c_k,\mathcal{F}[c^\dagger_m](k')\} &= \delta_{k,-k'}
    \label{eq:anticom-ckfck}
\end{align}
This explains what I mean by preserving the commutation relationship.
And, in the second approach, the inverse fourier transformation is also
different:
\begin{align}
    c_m &= \sum_k e^{ikm} c_k \\
    c^\dagger_m &= \sum_k e^{-ikm} c^\dagger_k
\end{align}

Below we make several remarks.
\begin{remark}
    It should be noted that, if we start with defining
    \begin{equation}
        c^\dagger_k \equiv \sum_m e^{-ikm} c^\dagger_m
    \end{equation}
    Then, we would have, instead of eq.\ref{eq:fourier-ck}
    \begin{equation}
        c_k \equiv \sum_m e^{ikm} c_m
    \end{equation}
\end{remark}

\begin{remark}
    It should also be noted that, mathematically we have the theorem:
    \begin{equation}
        \mathcal{F}[f^*(m)](k) = (\mathcal{F}[f(m)])^*(-k)
    \end{equation}
    Although, it deals only with complex conjugation, here we could analogously
    regard the theorem as if $*$ is $\dagger$. Therefore,
    \begin{equation}
        \mathcal{F}[c^\dagger_m](k) = c^\dagger_{-k}
    \end{equation}
    which explains eq.\ref{eq:anticom-ckfck} from another aspect.
\end{remark}

\begin{remark}
    Lastly, let's don't forget that the same fact hold with bosons operators, with
    $\{,\}\overset{\text{replaced by}}{\to}[,]$.
\end{remark}

\subsection{Miscellaneous}
\label{sec:Miscellaneous}

\paragraph{Transpose in Q.M.}

Transpose is somehow rare in quantum mechanics. Consider a complete
basis $\ket{n}$. By definition of adjoint (dagger), one has
\begin{equation}
    \braket{ An|m }=\braket{n | A^\dagger m}
\end{equation}
Also, one has
\begin{equation}
    \braket{ An|m } = \braket{ m|An }^*
\end{equation}
so
\begin{equation}
    \braket{ n|A^\dagger m } = \braket{ m|An }^* = \braket{ m|A|n }^*
\end{equation}
By this one sees that the operator $\dagger$ is transpose conjugate.
Therefore, the transpose of an operator $A$ is an operator
$\tensor[^t]{A}{}$ such
\begin{equation}
    \braket{ n|\tensor[^t]{A}{}|m } = \braket{ m|A|n }
\end{equation}
